\LARGE \bf Object Detection-Based Behaviour using Deep-Learning on Thymio

### 2018-06-01 paper/paper.tex
addeddguide

\title{\LARGE \bf
Object Detection-Based Behaviour using YOLO on Thymio
}

%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
%         \thanks{*Use the $\backslash$thanks command to put information here}\\
%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
%         University of Twente\\
%         7500 AE Enschede, The Netherlands\\
%         {\tt\small h.kwakernaak@autsubmit.com}}
%         \hspace*{ 0.5 in}
%         \parbox{3 in}{ \centering Pradeep Misra**
%         \thanks{**The footnote marks may be inserted manually}\\
%        Department of Electrical Engineering \\
%         Wright State University\\
%         Dayton, OH 45435, USA\\
%         {\tt\small pmisra@cs.wright.edu}}
%}

\author{Francesco Saverio Zuppichini$^{1}$ and Alessia Ruggeri$^{2}$}% <-this % stops a space

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The ability to classify objects in both space and domain is encoded in an enormous variety of species on the planet. Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results. With this paper, we propose a minimal architecture to archive the same goal using a cheap two-wheels robot, the Thymio, with a mounted frontal camera in order to make it act based on the objects detected in the surrounding. 
\end{abstract}

@@

The following endpoints are available:
\begin{lstlisting}
GET /model
POST /prediction  --image --size --compress
\end{lstlisting}
Each of them returns a JSON serialised response. The \texttt{/model} endpoint is used to get information about the model. These information are the classes that can be predicted and the colour associated to each one of them. It follows a response sample:
\begin{lstlisting}
{
    "classes": [ "person", "bicycle", "car", "motorbike", "aeroplane", ... ]
    "colors": [[255, 38, 0], [0, 63, 255], ... ]   
 }
\end{lstlisting}
The client can get a prediction by sending an image to \texttt{/prediction}. It is also possible to specify if the image is compressed or not and if the server should resize it before feeding it to the model. In our case, we send a compressed image directly taken from the MightyThymio after subscribing to the \texttt{/camera/compressed} topic and we define the resized size to (190,190). The small size is due to the low computational power since we had no access to a GPU. By sanding the same image showed in Figure \ref{fig: yolo-example} we get the following response.
\begin{lstlisting}
{'res': [{'boxes': [96.21580505371094,
                    219.6134033203125,
                    437.66387939453125,
                    594.16748046875],
          'class': 'bicycle',
          'class_idx': 1,
          'score': 0.48406994342803955}, ...
         ]
 'time': 0.174407958984375}
\end{lstlisting}
For each detected class we return the bounding boxes, the \texttt{boxes} key of the JSON, the class name, its index, and the score, that is the confidence of the model. Each box is composed by the top, left, bottom and right offsets of the bounding box with respect to the left and the top of the image. In the above example, the bicycle's bounding starts at $96$ pixels from the left and at $219$ pixels from the top.

@@

\includegraphics[width=0.25\linewidth]{images/leds/1}	
\includegraphics[width=0.25\linewidth]{images/leds/2}	
\includegraphics[width=0.25\linewidth]{images/leds/3}	
\end{center}
\begin{center}
\includegraphics[width=0.25\linewidth]{images/leds/4}	
\includegraphics[width=0.25\linewidth]{images/leds/5}
\end{center}
\caption{On board LEDs}
\end{figure}
\section{Conclusion}
In this paper, we presented a light and scalable architecture that uses a real-time Object Detection model to correctly find objects in the surrounding environment and to perform actions based on them. Moreover, because the only  hardware constraint is the camera, our work can be used into similar robots running ROS  to extend their functionalities. Furthermore, since we used YOLO to perform the classification task, the model can be easily re-trained with other classes to increase the context domain. This symbiosis between Machine Learning and Robotics highlights the power of both areas by creating new interesting use cases and scenarios in which both disciplines can shine.

>>>>

\title{\LARGE \bf
Object Detection-Based Behaviour using Deep-Learning on Thymio
}

\author{Francesco Saverio Zuppichini$^{1}$ and Alessia Ruggeri$^{2}$% <-this % stops a space
\thanks{$^{1}$Francesco Saverio Zuppichini, \href{mailto:zuppif@usi.ch}{zuppif@usi.ch} , AI master student at Università della Svizzera Italiana }%
\thanks{$^{2}$Alessia Ruggeri, \href{mailto:ruggea@usi.ch}{ruggea@usi.ch} , AI master student at Università della Svizzera Italiana }%
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The ability to classify objects in both space and domain is encoded in an enormous variety of species on the planet. Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results. With this paper, we propose a minimal architecture to archive the same goal using a cheap two-wheels robot, the Thymio, with a mounted frontal camera in order to make it moves based on the objects detected in the surrounding. 
\end{abstract}

@@

The following endpoints are available:
\begin{lstlisting}
GET /model
POST /prediction  --image --size --compress
\end{lstlisting}
Each of them returns a JSON serialised response. The \texttt{/model} endpoint is used to get information about the model. This information are the classes that can be predicted and the colour associated to each one of them. It follows a response sample:
\begin{lstlisting}
{
    "classes": [ 
    "person", 
    "bicycle", 
    "car", 
    "motorbike", 
    "aeroplane", ... ]
    "colors": [[255, 38, 0], [0, 63, 255], ... ]   
 }
\end{lstlisting}
The client can get a prediction by sending an image to \texttt{/prediction}. It is also possible to specify if the image is compressed or not and if the server should resize it before feeding it to the model. In our case, we send a compressed image directly taken from the MightyThymio after subscribing to the \texttt{/camera/compressed} topic and we define the resized size to (190,190). The small size is due to the low computational power since we had no access to a GPU. By sanding the same image showed in Figure \ref{fig: yolo-example} we get the following response.
\begin{lstlisting}
{'res': [{'boxes': [96.21580505371094,
                    219.6134033203125,
                    437.66387939453125,
                    594.16748046875],
          'class': 'bicycle',
          'class_idx': 1,
          'score': 0.48406994342803955}, ...
         ]
 'time': 0.174407958984375}
\end{lstlisting}
For each detected class we return the bounding boxes, the \texttt{boxes} key of the JSON, the class name, its index, and the score, that is the confidence of the model. Each box is composed by the top, left, bottom and right offsets of the bounding box with respect to the left and the top of the image. In the above example, the bicycle's bounding starts at $96$ pixels from the left and at $219$ pixels from the top.

@@

\includegraphics[width=0.25\linewidth]{images/leds/1}	
\includegraphics[width=0.25\linewidth]{images/leds/2}	
\includegraphics[width=0.25\linewidth]{images/leds/3}	
\end{center}
\begin{center}
\includegraphics[width=0.25\linewidth]{images/leds/4}	
\includegraphics[width=0.25\linewidth]{images/leds/5}
\end{center}
\caption{On board LEDs}
\end{figure}
A video showing the point of view of the Thymio while moving towards a \emph{cup} can be found at

\section{Conclusion}
In this paper, we presented a light and scalable architecture that uses a real-time Object Detection model to correctly find objects in the surrounding environment and to perform actions based on them. Moreover, because the only  hardware constraint is the camera, our work can be used into similar robots running ROS  to extend their functionalities. Furthermore, since we used YOLO to perform the classification task, the model can be easily re-trained with other classes to increase the context domain. This symbiosis between Machine Learning and Robotics highlights the power of both areas by creating new interesting use cases and scenarios in which both disciplines can shine.
